DS Tuc b is Aligned?

### 2019-09-02 paper/main.tex
notes on discussion

\subsubsection{RM as a powerful technique for young stars}

@@

@@

\software{%
    numpy \citep{numpy},
    matplotlib \citep{matplotlib},
    scipy \citep{Jones01}
    astropy \citep{Astropy18},
    eleanor \citep{Feinstein19},
    starry \citep{Luger19},
    exoplanet \citep{Foreman-Mackey19},
    theano
    }

>>>>

\subsection{RM as a powerful technique for young stars}

@@

\subsubsection{What about oblateness and differential rotation?}

Oblateness - how oblate is the star anyway?
Not important for these systems, just infer a different orbital velocity or radius, depending on how its fit. The only place to learn a difference is in ingress/egress, which needs to be resolved at a high timescale. Need a precise stellar radius and eccentricity, at which point it might be useful! But this is hard for these s

Differential rotation not mentionable unless system hystems already.ighly misaligned. Even then the signal is smaller than the scatter due to starspots so many observations will be required to disentangle.

@@

\software{%
    numpy \citep{numpy},
    matplotlib \citep{matplotlib},
    scipy \citep{Jones01}
    astropy \citep{Astropy18},
    eleanor \citep{Feinstein19},
    starry \citep{Luger19},
    theano
    }
